---
title: Data Storage
categories: [policy, data]
listing:
  - id: see-also
    type: table
    contents: ['index.qmd', 'classification.qmd']
    fields: ['title', 'categories']
---

The Data Team hosted different kinds of data in several locations: data to be used by research scientists at the Center or beyond is on [Box](https://nyu.app.box.com/), and internal data to the Data Team needed for the data processing pipeline is on [GIN](https://gin.g-node.org/). Sensitive credentials are stored on Box.

## Box

The Data Team maintained two primary folders on Box: `Data` and `data-team`. All deputy directors maintain "Co-Owner" permissions for each of these folders.

### `Data`

All datasets for end-use are located in [`Data`](https://nyu.app.box.com/folder/147034807624). The folder structure for `Data` follows this scheme:

```
Data/
  [project-slug]/
    raw/
      ...
    exports/
      ...
    nightly/
      ...
    rc/
      ...
    reuse/
      ...
```

The nomenclature employed within its project folder follows the [data stage scheme](https://nyuglobalties.github.io/dt-handbook/curation/storage.html). Access guidelines for each data stage are also provided in the handbook.

#### Project IDs

<!-- Data Project slugs README -->
```{r, echo=FALSE, results='asis'}
md_lines <- readLines(here::here("management/data-project-slugs/README.md"))

md_lines |>
  tail(n = length(md_lines) - 1) |>
  paste0(collapse = "\n") |>
  knitr::raw_output(markers = c("", ""))
```

### `data-team`

All Data Team auxiliary files (credentials, planning documents, reports, etc) are stored in [`data-team`](https://nyu.app.box.com/folder/141355112641). The folder structure for `data-team` is as follows:

```
credentials/
  ...
data/
  ...
misc/
  ...
planning/
  okrs/
    ...
  scoping/
    ...
reports/
  ...
```

#### `credentials`

<!-- credentials README -->
```{r, echo=FALSE, results='asis'}
md_lines <- readLines(here::here("management/credentials-info/README.md"))

md_lines |>
  tail(n = length(md_lines) - 1) |>
  paste0(collapse = "\n") |>
  knitr::raw_output(markers = c("", ""))
```

## GIN

[GIN](https://gin.g-node.org) is a data version control system freely available for researchers in neuroscience and related fields, hosted at the [Ludwig-Maximilians University of Munich](https://neuro.bio.lmu.de/). This data store is primarily used for data version and intermediate processing for the [`data-processing`](../guides/data-processing.qmd) project. Its primary audience is those who wish to contribute code to `data-proc` for the purpose of keeping all data asset production in the same location.

The data files are [located in this repository](https://gin.g-node.org/nyuglobalties/data). The directory structure follows that of the [data scheme](classification.qmd) used [above](#box).

## Dataverse

Published data, for reuse or replication, is located on the [Harvard Dataverse](https://dataverse.harvard.edu/dataverse/global-ties-for-children) following our [data curation standards](../curation/dataset_curation.qmd). Administrative access to TIES' dataverse is provided to all members of the deputy directorate.
